---
title: "Lab 3"
author: "Hannah Irish"
date: "2023-01-26"
output: html_document
---

```{r setup, echo=TRUE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(GGally)
library(jtools)
library(AICcmodavg)
```

```{css, echo=FALSE}
h1 {
  text-align: center;
}
```

# Pseudocode
 * Examine our data (plots, tables, summary stats)
 * Identify a question
 * Wrangle the data (if necessary)
 * Identify some candidate models
 * Select among candidate models using AIC/BIC
 * Select among candidate models using k-fold cross validation
 * Select among candidate models using area under Receiver Operating Characteristic Curve
  
 
```{r, warning=FALSE, message=FALSE}

GGally::ggpairs(penguins %>% select(species, bill_length_mm:sex), 
                aes(color=species))
```


```{r}
#class(penguins$species)
#evels(penguins$species)

adelie_chinstrap <- penguins %>%
  filter(species %in% c("Adelie", "Chinstrap")) %>%
  mutate(species = fct_drop(species)) %>% ##drop any levels that no longer exist
  select(-year) %>%
  drop_na()



```
## Let's check out the trends across variables

```{r}
ggplot(data = adelie_chinstrap, aes(x=body_mass_g, y=flipper_length_mm)) +
  geom_point(aes(color=sex, shape = island))+
  facet_wrap(~ species)

ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y=bill_length_mm)) +
  geom_point(aes(color=sex, shape = island)) +
  facet_wrap(~ species)
```

## Let's do some binary logistic regression

```{r}
f1 <- species ~ body_mass_g + flipper_length_mm + sex

ad_chin_blr1 <- glm(f1, data=adelie_chinstrap, family="binomial")
  
  
```









