---
title: "Lab 3"
author: "Hannah Irish"
date: "2023-01-26"
output: html_document
---

```{r setup, echo=TRUE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(GGally)
library(jtools)
library(AICcmodavg)
```

```{css, echo=FALSE}
h1 {
  text-align: center;
}
```

# Pseudocode
 * Examine our data (plots, tables, summary stats)
 * Identify a question
 * Wrangle the data (if necessary)
 * Identify some candidate models
 * Select among candidate models using AIC/BIC
 * Select among candidate models using k-fold cross validation
 * Select among candidate models using area under Receiver Operating Characteristic Curve
  
 
```{r, warning=FALSE, message=FALSE}

GGally::ggpairs(penguins %>% select(species, bill_length_mm:sex), 
                aes(color=species))
```


```{r}
#class(penguins$species)
#evels(penguins$species)

adelie_chinstrap <- penguins %>%
  filter(species %in% c("Adelie", "Chinstrap")) %>%
  mutate(species = fct_drop(species)) %>% ##drop any levels that no longer exist
  select(-year) %>%
  drop_na()



```
## Let's check out the trends across variables

```{r}
ggplot(data = adelie_chinstrap, aes(x=body_mass_g, y=flipper_length_mm)) +
  geom_point(aes(color=sex, shape = island))+
  facet_wrap(~ species)

ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y=bill_length_mm)) +
  geom_point(aes(color=sex, shape = island)) +
  facet_wrap(~ species)
```

## Let's do some binary logistic regression

```{r}
f1 <- species ~ body_mass_g + flipper_length_mm + sex

ad_chin_blr1 <- glm(formula = f1,
                    data = adelie_chinstrap,
                    family = "binomial")

#summary(ad_chin_blr1)  

blr1_tidy <- tidy(ad_chin_blr1)
```

```{r}
ggplot(data=adelie_chinstrap, aes(x=species, y=flipper_length_mm)) +
  geom_jitter(aes(color=sex)) 
```



```{r}
blr1_fitted<- ad_chin_blr1 %>% 
  broom::augment(type.predict = "response")

ggplot(data=blr1_fitted, aes(x=flipper_length_mm, y=  .fitted)) +
  geom_point(aes(color=sex, shape = species)) +
  geom_smooth(aes(color=sex), se=FALSE) +
  labs(x="Flipper Length (mm)", y = "Probability of outcome(Chinstrap)")

```

## Predictions for new values with predict()

```{r}
ex_1 <- predict(ad_chin_blr1,
                data.frame(sex = "female",
                  body_mass_g = 3410,
                  flipper_length_mm = 192),
                # tell it type = 'response' to get prob, not log odds
                type = "response")
 
new_df <- data.frame(
  sex = c("male", "male", "female"),
  body_mass_g = c(3298, 4100, 3600),
  flipper_length_mm = c(212, 175, 180)
)
 
ex_2 <- predict(ad_chin_blr1,
            	    new_df,
            	    type = "response")

```


## Create a new binary logisitic model

```{r}
f2 <- species ~ bill_length_mm + body_mass_g

ad_chin_blr2 <- glm(formula = f2, data = adelie_chinstrap, family = "binomial")

ad_chin_blr2


blr2_tidy <- broom::tidy(ad_chin_blr2)
```
```{r}
ggplot(data=adelie_chinstrap, aes(x=bill_length_mm, y=body_mass_g)) +
  geom_point(aes(color=species))
```


## Model selection
```{r}
AICcmodavg::aictab(list(ad_chin_blr1, ad_chin_blr2))

##log likelihood is a smaller negative number in model 2 -- that's what's making this model way better

AICcmodavg::bictab((list(ad_chin_blr1, ad_chin_blr2)))


```
## 10-fold cross validation

```{r}
set.seed(123)

n_folds <- 10

fold_vec <- rep(1:n_folds, length.out = nrow(adelie_chinstrap))

ad_chin_kfold <- adelie_chinstrap %>%
  mutate(fold = sample(fold_vec, size=n(), replace=FALSE))



```


purrr::map()
```{r}

x_vec <- 1:10
thing <- purrr::map(.x = x_vec, ### a sequence(vector, list))
                   .f = sqrt) ## a funtion
#thing

## using our own function

my_func <- function(x, y, z) {
  return((x-y)^z)
}

thing2 <- purrr::map(.x = x_vec,
                     .f = my_func,
                     y=2, z=3)

#thing2


```

``` {r}
# function to calculate accuracy, given a "truth" vector and "prediction" vector
pred_acc <- function(x, y) {
  accurate <- ifelse(x == y, 1, 0)
  
  return(mean(accurate, na.rm = TRUE))
}

# function to calculate accuracy of BLR of one fold (training and testing)
calc_fold <- function(i, fold_df, f) {
  kfold_test <- fold_df %>%
    filter(fold == i)
  kfold_train <- fold_df %>%
    filter(fold != i)
  
  kfold_blr <- glm(f, data = kfold_train, family = 'binomial')
  kfold_pred <- kfold_test %>%
    mutate(blr = predict(kfold_blr, kfold_test, type = 'response')) %>%
    mutate(pred = ifelse(blr > 0.50, 'Chinstrap', 'Adelie'))
  
  kfold_accuracy <- kfold_pred %>%
    summarize(blr_acc = pred_acc(species, pred)) # using my other function
  
  return(kfold_accuracy)
}

n_folds <- 10

results1_purrr_df <- purrr::map(.x = 1:n_folds, # sequence of fold numbers
                                .f = calc_fold, # function
                                fold_df = ad_chin_kfold, # additional argument to calc_fold()
                                f = f1) %>%              # additional argument to calc_fold()
  bind_rows() %>%
   mutate(mdl = 'f1')

results2_purrr_df <- purrr::map(.x = 1:n_folds, .f = calc_fold, 
                               fold_df = ad_chin_kfold,
                               f = f2) %>%
  bind_rows() %>%
  mutate(mdl = 'f2')

results_purrr_df <- bind_rows(results1_purrr_df, results2_purrr_df) %>%
  group_by(mdl) %>%
  summarize(mean_acc = mean(blr_acc))

results_purrr_df
```


# Tidymodels version

```{r, warning=FALSE}
### define model type
blr_model <- logistic_reg() %>%
  set_engine("glm")

### basic regression

blr_tidy_f1 <- blr_model %>%
  fit(f1, data = adelie_chinstrap)

blr_tidy_f2 <- blr_model %>%
  fit(f2, data = adelie_chinstrap)

blr_tidy_f1 %>%
  tidy()

blr_tidy_f2 %>%
  glance()

```


## TIdy kfold cross validation

```{r}
set.seed(345)

tidy_folds <- vfold_cv(adelie_chinstrap, v=10)

###use workflow to bundle a model and a formula
blr_tidy_wf1 <- workflow() %>%
  add_model(blr_model) %>%
  add_formula(f1)

blr_tidy_cv_f1 <- blr_tidy_wf1 %>%
  fit_resamples(tidy_folds)

collect_metrics(blr_tidy_cv_f1)
```

### Area under the curve
```{r}
blr_f1_pred <- adelie_chinstrap %>%
  mutate(predict(blr_tidy_f1,.)) %>%
  mutate(predict(blr_tidy_f1, .,type = "prob"))

blr_f1_pred %>%
  roc_curve(truth = species, .pred_Adelie) %>%
  autoplot()
```



